From correlation to causality: statistical approaches to learning regulatory relationships in large-scale biomolecular investigations

### 2015-12-09 manuscript/write_up.tex
olga todos

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
\usepackage{color}
\def\todo#1{{\color{red}[TODO: #1]}}
\def\added#1{{\color{magenta}[Added or edited: #1]}}

@@

\begin{abstract}
  Causal inference -- the task of uncovering regulatory relationships between components of biomolecular pathways and networks - is a primary goal of many high throughput investigations.  Statistical associations between quantitative measurements can reveal an enticing number of putative causal interactions, but when do such associations reflect the underlying causal biomolecular mechanisms?  The goal of this perspective is to provide suggestions for causal inference in large scale experiments, which utilize high throughput technologies such as mass spectrometry-based proteomics.  We describe in non-technical terms the pitfalls of inference in large datasets, and suggest methods to overcome these pitfalls and reliably find regulatory associations.
\end{abstract}

@@

Causal inference \cite{pearl2009causality} applied to 'omics experiments, elucidates statistical associations \added{(e.g. Pearson correlation, Spearman correlation, mutual information)}, which result from the underlying biomolecular mechanistic relationships. Modern high-throughput technologies such as mass spectrometry-based proteomics quantify components of the biomolecular systems on a large scale.  \added{Thus, the opportunity exists for the proteomics community to apply computational methods for causal inference developed for gene microarray data to proteomics data \cite{bensimon2012mass}.}

We will demonstrate the paradoxical result that the large amount of data generated by high-throughput proteomics experiments make the task of causal inference more difficult.  If only two biologically unrelated analytes were measured simultaneously, there is some probability of a spurious association -- an association between the analytes arising purely from random chance -- though the chance of this happening is low and gets lower as sample size increases. The difficulty of high-throughput data stems from the fact that the more analytes that are measured, the more pairwise associations between analytes are generated, resulting in a much greater chance for the appearance of spurious associations that are just as strong as associations that represent actual biological relationships.  This obfuscates the true signal, leading to increased false discoveries of putative causal events.  \added{While the gene network inference community has developed approaches to dealing with this issue\cite{bensimon2012mass} , the solutions specific to the experimental conditionals and biological questions relevant to proteomics are still in early stages.} The problem can be addressed by refining the biological question, and by improving experimental design in terms of selection of  (1) the subset of analytes, (2) the number of biological replicates, and (3) the type of biological conditions and stresses. Below, we describe in non-technical terms the process of elucidating causal associations from high-throughput data and suggest practical approaches for analysis of large scale \added{proteomics} datasets.

@@

\begin{figure}[!tpb]
\centerline{\includegraphics[width=1\textwidth]{figs/mapk.png}}
\caption{A: Overview of the 3 steps of causal inference, illustrated for the MAPK signaling cascade.    B, C, and D feature an experiment simulated from the Huang-Ferrell computational model of the phosphorylation cascade.  B: Pairwise plots of concentration values of phosphorylated (doubly phosphorylated for Mek and Erk) forms of each protein, and observed Spearman correlation values.  The Raf -- Erk correlation is high, despite the fact that Raf does not directly regulate Erk.  C: Concentrations of Raf versus Erk, where samples corresponding to high Mek are highlighted in circles.  The right panel of B shows the subset of samples with high Mek (i.e. conditional on Mek being high). In these samples the association between Raf and Erk disappears, indicating that Raf and Erk are {\it conditionally independent} given Mek.  D: After Raf is inhibited, the observed association between Raf and Mek remains, while the association between Mek and Erk disappears. A second simulation, which is similar to the previous one but incorporates the inhibition of Mek reveals the causal flow from Raf to Mek to Erk.
\label{mapkInference}}
\end{figure}

Figure \ref{mapkInference}A demonstrates the causal inference workflow starting with analysis of statistical associations in the data.  In step 1, a correlation graph between cascade components Raf, Mek, and Erk is assembled from the measurements of protein concentration.  Step 2 reduces the correlation graph to a sparse graph of conditional dependencies (Raf--Mek, and Mek--Erk).  Step 3 interrogates this graph to find putative causal relationships (Raf-->Mek, and Mek-->Erk).  While step 1 has little requirements, step 2 requires multiple samples or replicates, and step 3 requires systematic interventions (e.g. with protein inhibitors).

Figure \ref{mapkInference}B illustrates Step 1 of the causal inference, and shows 2-way plots of the protein concentrations across the biological samples, and Spearman correlations to quantify the extent of the associations.  The correlation values are high, and would meet most reasonable cut-off thresholds for constructing the correlation network in the left part of panel A.  The Raf--Mek and the Mek--Erk correlation edges match the Raf-->Mek, Mek-->Erk known causal edges.  What about the noncausal Raf--Erk edge? Despite the high Raf--Erk correlation, there is no direct causal mechanism between them (aside from the one via Mek, which is already accounted for via the Raf-->Mek and Mek-->Erk edges).  In causal  inference, our goal is to eliminate this "nuisance" edge.  How is this done?

To describe Step 2 of causal inference, we introduce some terminology. In language of \added{probability} the quantified proteins are called {\it variables}. \added{When two proteins are connected in how they vary, such that knowing the behavior of one protein provides information on the other, they are called {\it dependent}.  If there is no such connection, they are called {\it independent}. {\it Conditional independence} is a special case that is important to causal inference.  Two dependent variables are conditionally independent if, after knowing, or {\it conditioning on} the behavior of third-party variables, they become independent -- knowing one provides no additional information about the other after the information from the third party variables is considered.}

\added{Causation and dependence are linked as follows;
\begin{itemize}
\item For two variables, if one is the direct cause of the other, they are dependent, even after conditioning on other variables in the system.
\item If the two variables that are not directly causal related, {\it more often than not are still dependent}, but that dependence disappears after conditioning on the other variables in the system.
\end{itemize}
Note {\it dependence} is a property of the underlying biology, and {\it statistical association} is a property of the data generated by the biology, they are not the same.  {\it Under the right measurement conditions} dependence manifests itself as statistical association in the data and application of statistical analysis can reveal cases of conditional independence (when those conditions breakdown is beyond the scope of this perspective, but Sachs and Itani et al. 2013 \cite{sachs2013single} explores this in detail within the phospho-proteomics context).  So if we had an oracle that revealed that two proteins are still dependent after conditioning on all others, then we'd know they were one of them was a direct causal of the other.  Without an oracle, we must rely on statistical inference of cases where pairs of proteins were conditional independent, ignore those cases and focus on the remaining pairs as potential causal relations.  For a more rigorous treatment of the link between mechanism, probabilistic dependence, and statistics, consult Pearl's seminal work in this area\cite{pearl2009causality}.}

Let's see how this applies to the MAPK signaling cascade. \added{We know from the biology that Raf regulates the abundance of Erk though Mek.  Thus Raf and Erk are dependent.  However Erk abundance is directly determined by Mek, Raf does not exert any additional regulatory influence on Erk beyond its influence {\it through Mek}.  Thus Raf and Erk are conditionally independent given Mek.  This biology is manifests itself in the data.}  Figure \ref{mapkInference}C compares Raf to Erk, indicating in \added{solid circles} the biological samples where concentrations of Mek are high (here, set to the top quartile).   Note that when we subset the data to only the samples with high Mek, we can no longer visually detect the association between Raf and Erk.  \added{To understand why we'd interpret this as evidence for the presence of conditional independence between Raf and Mek, we can build intuition from a formal statistical test of conditional independence -- the null hypothesis is conditional independence between Raf and Erk given Mek, the quantification of association between Raf and Erk {\it after subsetting Mek} is the test statistic, and we decide in favor of the null hypothesis if the p-value for the test statistic (the probability an association at least as high as the one observed could have emerged spuriously) is too high.  Indeed, the class of causal inference algorithms called constraint-based algorithms repeatedly performs this type of test over multiple pairs of variables \cite{spirtes2000causation}. Given this evidence the edge between Raf and Erk is removed, resulting in the middle graph of Figure \ref{mapk}A.}

At Step 2 in the figure, the direction of the regulation remains unknown. Inference of the direction of the chain of events requires that the experimental design involves external interventions or stresses. Figure \ref{mapkInference}D illustrates the results of Step 3, in the case where an intervention targeted Mek with an inhibitor. The intervention does not affect the concentration of Mek, however it blocks its ability to phosphorylate other proteins.  After this intervention the Raf--Mek relationship is unchanged, while Erk drops to a low level.  From this we can infer that Mek has causal influence on Erk, and since Raf was unaffected by the intervention, that Raf has causal influence on Mek.  With the intervention, we can finally move from the undirected graph in panel A - step 2 to the causal graph in panel A - step 3.

In the general case, computational methods for causal inference follow the workflow  in Figure \ref{mapkInference}A, while scaling it to characterize multiple inter-related variables. Step 1 creates a dense network of pairwise associations. \added{Step 2 identifies cases of conditional independence and removes those edges in those cases to create a much sparser network.}  Finally, Step 3 uses the experimental design, specifically the information regarding the interventions, to evaluate these edges as evidence for potential causal events.  See Koller-Friedman \cite{koller2009probabilistic} for a detailed description of these methods and their theoretical underpinnings. Numerous implementations of these algorithms are available in statistical software, e.g. in the R package {\tt bnlearn} \cite{scutari2009learning}.

\section{II. Large-scale statistical inference of causal relationships: challenges of scaling up}

@@

We illustrate this problem with a computer simulation, inspired by Fan et. al \cite{fan2014challenges} but translated to our context. First, we simulated an experiment that quantifies the abundances of 20 proteins in 100 biological samples.  Second, we simulates another experiment where the number of proteins was increased to 500.  In both experiments the proteins are completely independent from each other, and each protein in each replicate is assigned a value randomly drawn from a Gaussian distribution. In other words, we do not expect any biologically meaningful associations in these data. We repeated each of these simulations 500 times. Figure \ref{spur_corr} shows for each experiment the histogram of the highest Pearson correlation across any pair of proteins in the 500 instances of the simulation. As can be seen, the experiment with 500 proteins produces relatively large maximum pairwise correlations, demonstrating that an increase in the number of proteins leads to an increase in spurious correlations.  This is clearly a problem when high Pearson correlation is used as an initial evidence of a biological function.

@@

Finally, Step 3 of the workflow requires interventions to infer causal relationships from evidence of conditional independence.  Quantifying a large number of analytes introduces a  challenge for this step as well. As the number of features grows, the number of interventions needed to fully infer causality grows, and eventually performing a sufficient perturbation experiments becomes infeasible.   We showed with the Raf-Mek-Erk example that one intervention was sufficient to infer two causal relationships. \added{Given theoretical work on the number of interventions necessary to fully elucidate causality between a set of variations\cite{eberhardt2012number}\cite{hauser2012two}\cite{hyttinen2013experiment}}, a set of interventions on $< k$ variables may be sufficient to infer causal events between $k$ analytes . Unfortunately, both the number of biological replicates and the number of interventions im high-throughput profiling experiments is typically small.  Also, if the step 2 results in too many false positives for potential causal relations, this will adversely affect the results of step 3 regardless of the size of the dataset.

@@

\item \textit{Consider broad-scale interventions}. Broad-scale interventions sacrifice specificity of targeted interventions to simultaneously perturb many variables in a biological system. One example of broad-scale interventions is varying experimental conditions, in order to activate multiple pathways.  Signals from endocrine, paracrine, and autocrine ligands elicit various signaling responses in hepatocytes, thus interventions that cover this range of signals gives the best picture of the broader causal network of hepatocyte signaling \cite{alexopoulos2010networks}. Similarly, interventions that go beyond receptor-level and perturb multiple components of the system bring cascading causal direct orientation deeper into the network.  Although they do not provide specific information about the downstream effects of stimulation,  broad-scale interventions can provide more causal insight. Therefore, the advantage of this approach is that it may enable elucidation of  causality across the entire system.

@@

This list suggests impactful approaches that can drastically improve causal inference from high-thoughput experiments, by constraining the inference task, and thus allowing for accurate
statistical inferences. For instance, the task of assessing which of all
the possible KEGG pathways is present in a dataset will be far less
error-prone than the task of assessing which of all possible
combinations of my measured variables might form a biological pathway.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
\usepackage{color}
\def\todo#1{{\color{red}[TODO: #1]}}
\def\added#1{{\color{blue} #1}}
\def\removed#1{{\color{magenta}[Removed: #1]}}
\def\note#1{{\color{cyan}[Note on edit: #1]}}

@@

\begin{abstract}
  Causal inference -- the task of uncovering regulatory relationships between components of biomolecular pathways and networks - is a primary goal of many high throughput investigations.  Statistical associations between quantitative measurements can suggest an enticing number of hypotheses regarding the underlying causal interactions. But when do such associations reflect the underlying causal biomolecular mechanisms?  The goal of this perspective is to provide suggestions for causal inference in large scale experiments, which utilize high throughput technologies such as mass spectrometry-based proteomics.  We describe in non-technical terms the pitfalls of inference in large datasets, and suggest methods to overcome these pitfalls and reliably find regulatory associations.
\end{abstract}

@@

%\note{Olga's comment: Modern experiments generate large scale data
%Correlation. Not enough. Causal inference elucidates.... or causal relationships  Examples are XXX However this is difficult because XXX}

\added{Modern high-throughput technologies such as mass spectrometry simultaneously quantify hundreds or even thousands of biomolecular analytes.  Statistical associations (e.g. Pearson correlation, Spearman correlation, and mutual information) between the analytes  can suggest an enticing number of hypotheses regarding the underlying causal biomolecular mechanism.  However, associations do not imply causation. Formal methods of causal inference \cite{pearl2009causality} \todo{Could you also reference http://www.biomedcentral.com/1471-2105/8/S6/S5} are required to probe these statistical associations for causality, and infer the underlying regulatory mechanisms. }

\added{There is an increasing interest in causal inference in proteome research. It has previously been used to learn the directed structure of signal transduction networks, e.g. in flow cytometry investigations in Sachs et al. 2005 \cite{sachs2013single}, antibody/bead-based XMAP technology from Luminex in Saez-Rodriguez et al. 2009\cite{saez2009discrete} and others \todo{what do you mean by 'others'? Other technologies? Other authors? What did they do?} \cite{prill2011crowdsourcing}.
However, the successful examples of causal inference in proteomics are very few \cite{bensimon2012mass}. In this perspective we demonstrate that this is not an accident, because large numbers of quantified analytes can make the task of causal inference more difficult.  The difficulty stems from the fact that large numbers of quantified analytes  lead to more spurious pairwise associations, obfuscate the true signal, and increase the false discoveries of putative causal events. Below we describe in non-technical terms the process of elucidating causal associations from high-throughput data, and suggest practical approaches for causal inference in large scale proteomic datasets.  Specifically, we suggest that the task of causal inference can be facilitated by refining the biological question, and by improving experimental design in terms of selection of  (1) the subset of analytes, (2) the number of biological replicates, and (3) the type of biological conditions and stresses. }

@@

\begin{figure}[!tpb]
\centerline{\includegraphics[width=1\textwidth]{figs/mapk.png}}
\caption{A: Overview of the 3 steps of causal inference, illustrated for the MAPK signaling cascade.    B, C, and D feature an experiment simulated from the Huang-Ferrell computational model of the phosphorylation cascade.  B: Pairwise plots of concentration values of phosphorylated (doubly phosphorylated for Mek and Erk) forms of each protein, and observed Spearman correlation values.  The Raf -- Erk correlation is high, despite the fact that Raf does not directly regulate Erk.  C: Concentrations of Raf versus Erk, where samples corresponding to high Mek (here, set to the top quartile) are highlighted \added{with filled circles}.  The right panel of C shows the subset of samples with high Mek (i.e. conditional on Mek being high). In these samples the association between Raf and Erk disappears, \added{and we infer} that Raf and Erk are {\it conditionally independent} given Mek.  D: After Raf is inhibited, the observed association between Raf and Mek remains, while the association between Mek and Erk disappears. A second simulation, which is similar to the previous one but incorporates the inhibition of Mek reveals the causal flow from Raf to Mek to Erk. \todo{Where is this last simulation shown? If it's not shown, add (not shown) at the end of the sentence.}
\label{mapkInference}}
\end{figure}

Figure \ref{mapkInference}A demonstrates the causal inference workflow starting with analysis of statistical associations in the data.  In step 1, a correlation graph between cascade components Raf, Mek, and Erk is assembled from the measurements of protein concentration.  Step 2 reduces the correlation graph to a sparse graph of \added{inferred} underlying conditional dependencies (Raf--Mek, and Mek--Erk).  Step 3 interrogates this graph to find putative directions of causal relationships (Raf-->Mek, and Mek-->Erk).  While step 1 has little requirements, step 2 requires multiple samples or replicates, and step 3 requires systematic interventions (e.g. with protein inhibitors).

Figure \ref{mapkInference}B illustrates Step 1 of the causal inference, and shows 2-way plots of the protein concentrations across the biological samples, and Spearman correlations to quantify the extent of the associations.  The correlation values are high, and would meet most reasonable cut-off thresholds for constructing the correlation network in the left part of panel A.  The Raf--Mek and the Mek--Erk correlation edges match the Raf-->Mek, Mek-->Erk known causal edges.  What about the non-causal Raf--Erk edge? Despite the high Raf--Erk correlation, there is no direct causal mechanism between them (aside from the one via Mek, which is already accounted for via the Raf-->Mek and Mek-->Erk edges).  In causal  inference, our goal is to eliminate this ``nuisance" edge.  How is this done?

\added{To describe Step 2 of causal inference, we introduce some terminology. If concentrations of two proteins vary between the biological samples in a coordinated manner, such that knowing the behavior of one protein provides information on the other, the two proteins are called {\it dependent}. Otherwise they are called {\it independent}. {\it Conditional independence} is a special case that is important to causal inference.  Two {\it dependent} proteins are {\it conditionally independent} if, after knowing (in probability language, {\it conditioning on}) the behavior of third-party biomolecules, the two proteins become independent. In other words, knowing the concentration of one protein provides no information about the other after considering the information from the third party.}

\added{While statistical associations and correlations are properties of the observed data, dependence and conditional independence are properties of the underlying processes that generate the data. Step 2 relies on statistical inference\cite{pearl2009causality} to infer from the observed data pairs of proteins that are conditionally independent. The conditionally independent pairs are ignored, and the remaining pairs are kept as potential causal relations.}

Let's see how this applies to the MAPK signaling cascade. \added{Since Raf regulates the concentration of Erk, Raf and Erk are dependent.  However, since the concentration of Erk is directly determined by Mek, Raf does not exert any additional regulatory influence on Erk beyond its influence {\it through Mek}.  Thus Raf and Erk are conditionally independent given Mek.  }  Figure \ref{mapkInference}C illustrates the process of statistical inference by comparing the concentrations of Raf and Erk. When we subset the measurements to only the samples with high Mek, we can no longer see the association between Raf and Erk. Formally, the algorithms repeatedly test the null hypothesis of conditional independence between Raf and Erk given Mek, and makes the decision based on p-values\cite{spirtes2000causation}. Given this evidence the edge between Raf and Erk is removed, resulting in the middle graph of Figure \ref{mapk}A.

\added{At Step 2 in the figure,} the direction of the regulation remains unknown. Inference of the direction of the chain of events requires that the experimental design involves external interventions or stresses. Figure \ref{mapkInference}D illustrates the results of Step 3, in the case where an intervention targeted Mek with an inhibitor. The intervention does not affect the concentration of Mek, however it blocks its ability to phosphorylate other proteins.  After this intervention the Raf--Mek relationship is unchanged, while Erk drops to a low level.  From this we can infer that Mek has causal influence on Erk, and since Raf was unaffected by the intervention, that Raf has causal influence on Mek.  With the intervention, we can finally move from the undirected graph in panel A - step 2 to the causal graph in panel A - step 3.

\added{Causation and dependence are linked as follows;
\begin{itemize}
\item For two proteins, if one is the direct cause of the other, they are dependent, even after conditioning on other proteins in the system.
\item If the two proteins that are not directly causal related, {\it more often than not are still dependent}, but that dependence disappears after conditioning on the other proteins in the system.
\end{itemize}}

In the general case, computational methods for causal inference follow the workflow  in Figure \ref{mapkInference}A, while scaling it to characterize multiple inter-related proteins. Step 1 creates a dense network of pairwise associations. \removed{Step 2 reduces this dense network to a sparse network of putative conditional dependencies, using empirical evidence of conditional independence between pairs of proteins.} \added{Step 2 identifies cases of conditional independence and removes those edges in those cases to create a much sparser network.}  Finally, Step 3 uses the experimental design, specifically the information regarding the interventions, to evaluate these edges as evidence for potential causal events.  See Koller-Friedman \cite{koller2009probabilistic} for a detailed description of these methods and their theoretical underpinnings. Numerous implementations of these algorithms are available in statistical software, e.g. in the R package {\tt bnlearn} \cite{scutari2009learning}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{II. Large-scale statistical inference of causal relationships: challenges of scaling up}

@@

We illustrate this problem with a computer simulation, inspired by Fan et. al \cite{fan2014challenges} but translated to our context. First, we simulated an experiment that quantifies the concentrations of 20 proteins in 100 biological samples.  Second, we simulates another experiment where the number of proteins was increased to 500.  In both experiments the proteins are completely independent from each other, and each protein in each replicate is assigned a value randomly drawn from a Gaussian distribution. In other words, we do not expect any biologically meaningful associations in these data. We repeated each of these simulations 500 times. Figure \ref{spur_corr} shows for each experiment the histogram of the highest Pearson correlation across any pair of proteins in the 500 instances of the simulation. As can be seen, the experiment with 500 proteins produces relatively large maximum pairwise correlations, demonstrating that an increase in the number of proteins leads to an increase in spurious correlations.  This is clearly a problem when high Pearson correlation is used as an initial evidence of a biological function.

@@

Finally, Step 3 of the workflow requires interventions to infer causal relationships from evidence of conditional independence.  Quantifying a large number of analytes introduces a  challenge for this step as well. As the number of features grows, the number of interventions needed to fully infer causality grows, and eventually performing a sufficient perturbation experiments becomes infeasible.   We showed with the Raf-Mek-Erk example that one intervention was sufficient to infer two causal relationships. \added{Given theoretical work on the number of interventions necessary to fully elucidate causality between a set of variations\cite{eberhardt2012number}\cite{hauser2012two}\cite{hyttinen2013experiment}}, a set of interventions on $< k$ proteins may be sufficient to infer causal events between $k$ analytes . Unfortunately, both the number of biological replicates and the number of interventions im high-throughput profiling experiments is typically small.  Also, if the step 2 results in too many false positives for potential causal relations, this will adversely affect the results of step 3 regardless of the size of the dataset.

@@

\item \textit{Consider broad-scale interventions}. Broad-scale interventions sacrifice specificity of targeted interventions to simultaneously perturb many proteins in a biological system. One example of broad-scale interventions is varying experimental conditions, in order to activate multiple pathways.  Signals from endocrine, paracrine, and autocrine ligands elicit various signaling responses in hepatocytes, thus interventions that cover this range of signals gives the best picture of the broader causal network of hepatocyte signaling \cite{alexopoulos2010networks}. Similarly, interventions that go beyond receptor-level and perturb multiple components of the system bring cascading causal direct orientation deeper into the network.  Although they do not provide specific information about the downstream effects of stimulation,  broad-scale interventions can provide more causal insight. Therefore, the advantage of this approach is that it may enable elucidation of  causality across the entire system.

@@

This list suggests impactful approaches that can drastically improve causal inference from high-thoughput experiments, by constraining the inference task, and thus allowing for accurate
statistical inferences. For instance, the task of assessing which of all
the possible KEGG pathways is present in a dataset will be far less
error-prone than the task of assessing which of all possible
combinations of my measured proteins might form a biological pathway.
